---
title: "Varroa cage trialsr"
author: "Reed Johnson"
date: "9/27/2022"
output: html_document
---

## Install libraries
```{r setup, include=FALSE, cache = FALSE}
require("knitr")
knitr::opts_chunk$set(echo = TRUE)
library(lubridate) # Deal with dates
library(plyr) #summarize by dates
library(dplyr) # remove duplicates
library(ggplot2) # plotting
library(googlesheets4) ## Read from GoogleDocs https://googlesheets4.tidyverse.org/
```

## Download GoogleSheet with data
```{r sheet_download}
gs4_deauth() ## Prevents google authorization; Needed for remote session (but keys must be used and sheets must be shared to anyone)
## Download data from all worksheets in google doc sheet
googleSheetsKey <- "1AzRyUUbEpHJjfKzXyccBazxftDhepGJGj31zzdPzrK4" #https://docs.google.com/spreadsheets/d/1AzRyUUbEpHJjfKzXyccBazxftDhepGJGj31zzdPzrK4/edit#gid=0
varroa_ss <- gs4_get(googleSheetsKey)
cage <- as.data.frame(read_sheet(googleSheetsKey, sheet = "Mortality"))
wash <- 

```
## Set working directory and load manually annotated label files
## Set dirname


write.csv(labels, file=paste(dirname, "summary.csv", sep="_"))

```

## Generate summaries
```{r summary}
## Set directory as working directory
setwd(paste("./label-output/", dirname, sep=""))

pdf(file=paste(dirname, "_Hour.pdf", sep=""))
plot(factor(hour(labels[labels$label == "combine",]$dateTime_start)), ylab="Detections per Hour", xlab="Hour", main=paste("Combine", dirname, sep=" "))
plot(factor(hour(labels[labels$label == "traffic",]$dateTime_start)), ylab="Detections per Hour", xlab="Hour", main=paste("Traffic", dirname, sep=" "))
plot(factor(hour(labels[labels$label == "bee",]$dateTime_start)), ylab="Detections per Hour", xlab="Hour", main=paste("Bee", dirname, sep=" "), drop=FALSE)
plot(factor(hour(labels[labels$label == "insect",]$dateTime_start)), ylab="Detections per Hour", xlab="Hour", main=paste("Insect", dirname, sep=" "))
dev.off()

## Summarize by hour (https://stackoverflow.com/questions/28879985/get-aggregate-sum-of-data-by-day-and-hour)
labels$hour <- factor(hour(labels$dateTime_start))
labels$date <- date(labels$dateTime)
labels_by_hour <- labels %>%
   group_by(field, date, hour, label) %>%
   # summarise(duration=sum(duration)) # Sum over duration
   summarise(count=length(label)) # Counts for each label

write.csv(labels_by_hour, file=paste(dirname, "labels_by_hour.csv", sep="_"))
```

```{r plot}
## Set directory as working directory
setwd(paste("./label-output/", dirname, sep=""))

pdf(file=paste(dirname, "Bee_HourV2.pdf", sep=""))
labels_by_hour_bee <- labels_by_hour[labels_by_hour$label=="bee",]
ggplot(labels_by_hour_bee, aes(hour, count)) +    # Create barchart without 0-levels
  geom_bar(stat = "identity", fill="gray", color="gray") + 
  labs(title=paste("Bee", dirname, sep=" ")) +
  scale_x_discrete(drop = FALSE)
dev.off()

```


